|

### 2023-01-11 paper.Rmd
Wed Jan 11 19:00:10 CET 2023: update-remote.sh

<!--- 
chatGPT
---

Q: what is pre-training in deep learning?
A: Pre-training in deep learning refers to the process of training a deep learning model on a large dataset before using it for a specific task. The goal of pre-training is to create a model that has a strong general understanding of the data and can be fine-tuned for a specific task.

Pre-training can be done in two ways: unsupervised pre-training and supervised pre-training. In unsupervised pre-training, the model is trained on a large dataset without labels, using techniques such as self-supervised learning or generative adversarial networks (GANs) to learn the underlying patterns in the data. In supervised pre-training, the model is trained on a large dataset with labels, using a supervised learning algorithm to learn the relationship between the input data and the corresponding labels.

Pre-training has several benefits. It can help improve the performance of the model on the target task by providing it with a better initial set of weights. It can also speed up training by reducing the amount of data and computational resources needed to train the model from scratch. Additionally, pre-trained models can be used as a starting point for transfer learning, allowing you to leverage the knowledge and experience of the pre-trained model for a new task.

Overall, pre-training is an important technique in deep learning that can help improve model performance and efficiency. It is commonly used in natural language processing and computer vision applications, where large amounts of labeled data are available.
-->

@@

```{bash compile_airfoil_2hl_maxIndSize_fullRun_30gens, include=FALSE}

@@

![Best Fitness over 30 Generations - Airfoil](./img/airfoil_FullRun_30gens/mean_median_fitness_byGens.png)

![Best Fitness Distribution after 30 Generations - Airfoil](./img/airfoil_FullRun_30gens/final_fit_boxplot.png)
lalal

@@

@@

![Statutory Declaration](./private/erklaerung.pdf)\

-->

>>>>

@@

```{bash compile_symReg_fullRun_30gens, include=FALSE}

@@

![Best Fitness over 30 Generations - Airfoil](./img/airfoil_2hl_maxIndSize_fullRun_30gens_withGP/mean_median_fitness_byGens.png)

![Best Fitness Distribution after 30 Generations - Airfoil](./img/airfoil_2hl_maxIndSize_fullRun_30gens/final_fit_boxplot.png)
lalal

@@

The experiments was repeated using the same setup with the only difference being a reduction from two hidden layers to 1 hidden layer.

![Best Fitness over 30 Generations - 1 hidden Layer - Airfoil](./img/airfoil_1hl_maxIndSize_fullRun_30gens/mean_median_fitness_byGens.png)

@@

![Statutory Declaration](./private/erklaerung.pdf)\
-->
